---
title: "Cleaning raw files"
output: html_notebook
---

```{r setup}
library(tidyverse)
library(quanteda)
library(RWeka)

#Load in appropriate dataset here
```


Steps for going in and out of arff for emotion words:
1) Get raw tweets
2) Lower case the tweets
3) Code covid tweets using keywords
4) Subset tweets if needed
5) Make text a character vector
6) Make created_at a date vector
7) Remove hashtags column
8) Turn is_quote and is_retweet into numeric variables
9) Remove line breaks using mutate(text = str_replace_all(text, "[\r\n]" , ""))
10) Write file as arff using foreign::write.arff
11) Read into Weka. Run filter.
12) Remove text and location variables
13) Save file
14) Load resulting file into R and merge with tweets dataset as necessary

Other notes to be aware of:
A) At some point in this process, R rounded status_id, making it useless as an id for each observation. For merging, etc, use a combination of user_id and created_at.

###Messy overview, more of a scratch pad

```{r}
data1 <- read.csv("./Data/electeds tweets 10-6-20.csv")
data2 <- read.csv("./Data/electeds tweets dec-04-20.csv")

data1 <- data1 %>% dplyr::select(user_id:followers_count)
data2 <- data2 %>% dplyr::select(user_id:followers_count)

data1 <- rbind(data1, data2)

data1 <- data1 %>% mutate(text2 = tolower(as.character(text)))


data1 <- data1 %>% mutate(covid_tweet = ifelse(grepl("covid | covid-19 | coronavirus | epidemic | pandemic | sars-cov-2 | wuhan | distanc* | #stayathome | #saferathome | shutdown | lockdown | lock* down | slow the spread | #slowthespread | physical* distanc* | social* distanc* | shelter in place | shelter-in-place | chin* virus | kung flu", as.character(data1$text2)) == TRUE, 1, 0))
data1 <- data1 %>% select(-hashtags)
data1 <- data1 %>% select(-text2)

covid_tweets <- data1 %>% filter(covid_tweet == 1)

covid_tweets <- covid_tweets %>% mutate(text = as.character(text))
covid_tweets <- covid_tweets %>% mutate(created_at = mdy_hms(created_at))
covid_tweets <- covid_tweets %>% mutate(is_quote = ifelse(is_quote == TRUE, 1, 0))
covid_tweets <- covid_tweets %>% mutate(is_retweet = ifelse(is_retweet == TRUE, 1, 0))


covid_tweets <- covid_tweets %>% mutate(text = str_replace_all(text, "[\r\n]" , ""))

write.csv(covid_tweets, "covid_tweets.csv")
foreign::write.arff(covid_tweets, "covid_tweets.arff")



covid_tweets <- read.csv("covid_tweets.csv")
emotions <- read.csv("covid_tweets2.csv")
covid_tweets <- arrange(covid_tweets, desc(status_id))




tweets_data <- covid_tweets %>% filter(is_quote == FALSE & is_retweet == FALSE) %>% dplyr::select(status_id, favorite_count, retweet_count, followers_count)

covid_tweets_data <- emotions %>% left_join(x = tweets_data, by = "status_id")


covid_tweets_data <- read.arff("covid_tweets.arff")

```



###Putting all text in lower case

```{r}
data1 <- data1 %>% mutate(text = tolower(text))
```


###Coding covid related tweets

```{r}
data1 <- data1 %>% mutate(covid_tweet = ifelse(grepl("covid | covid-19 | coronavirus | epidemic | pandemic | sars-cov-2 | wuhan | distanc* | #stayathome | #saferathome | shutdown | lockdown | lock* down | slow the spread | #slowthespread | physical* distanc* | social* distanc* | shelter in place | shelter-in-place | chin* virus | kung flu", data1$text) == TRUE, 1, 0))
```

###Inflammatory tweets (subset of covid)

CH note: I am not sure whether to include 'Wuhan', since it will also capture some non-racist early tweets about the virus. For now it is included.
```{r}
data1 <- data1 %>% mutate(inflammatory_covid_tweet = ifelse(grepl("wuhan | chin* virus | kung flu", data1$text) == TRUE, 1, 0))
```

###Economy tweets

```{r}
data1 <- data1 %>% mutate(economy_tweet = ifelse(grepl("business* | jobs | economy | reopen* | opening | relaunch | restart | workforce | economic | easing restrictions | operate | owners | recover*", data1$text) == TRUE, 1, 0))

```

###Saving overall dataset

```{r}
write.arff(data1, file = "./Data/elected_tweets_dec_04_20.arff")

```


###Saving covid tweets as a csv and arff

```{r}
covid_tweets <- data1 %>% filter(covid_tweet == 1)
write.csv(covid_tweets, "./Data/covid_tweets.csv")
write.arff(covid_tweets, file = "./Data/covid_tweets.arff")
```


